---
title: "draft_optimizer"
author: "Jake Berberian"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, include=FALSE}
library(tidyverse)
library(rvest)
library(glue)
```

# Initialize 

We want to initialize our league rules so our model can be league-specific. We'll start with Yahoo's default league settings. First up: rosters.  
```{r roster_rules}
number_teams <- 10
roster_size <- 15

# Number of players by position in starting lineup
QBs <- 1
WRs <- 2
RBs <- 2
TEs <- 1
FLEX <- 1
K <- 1
DST <- 1
```

Next, we'll focus on the most important part of fantasy- the scoring system. We'll start with kicking statistics. 
```{r kickers_scoring_system}
# FG19 indicates field goal from 0-19 yards out, FG29 from 20-29 yards, etc. 
FG19 <- 3
FG29 <- 3
FG39 <- 3
FG49 <- 4
FG50 <- 5
PAT <- 1

```

Then move to offensive points. 
```{r off_scoring}
# ppr = points per reception
ppr <- 0.5
pass_yards <- 0.04
pass_td <- 4
int <- -1
rush_yards <- 0.1
rush_td <- 6
# rpt_yards = reception yards
rpt_yards <- 0.1
rpt_td <- 6
return_td <- 6
# off_fmb_td = offensive fumble return TD. Doesn't happen too often, but just in case. 
off_fmb_td <- 6
# two_pt = two-point conversion
two_pt <- 2
fumble <- -2
```

And now, defensive.
```{r def_scoring}

```


# Data Import
We need some data to analyze, so we scraped data from [PFR](www.pro-football-reference.com). This can be found and run in the data_scrape.R script. 

```{r data_import, message=FALSE}

```





