---
title: "draft_optimizer"
author: "Jake Berberian"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library, include=FALSE}
library(tidyverse)
library(rvest)
library(glue)
```

# Initialize 

We want to initialize our league rules so our model can be league-specific. We'll start with Yahoo's default league settings. First up: rosters.  
```{r roster_rules}
number_teams <- 10
roster_size <- 15

# Number of players by position in starting lineup
QBs <- 1
WRs <- 2
RBs <- 2
TEs <- 1
FLEX <- 1
K <- 1
DST <- 1
```

Next, we'll focus on the most important part of fantasy- the scoring system. We'll start with kicking statistics. 
```{r kickers_scoring_system}
# FG19 indicates field goal from 0-19 yards out, FG29 from 20-29 yards, etc. 
FG19 <- 3
FG29 <- 3
FG39 <- 3
FG49 <- 4
FG50 <- 5
PAT <- 1

```

Then move to offensive points. 
```{r off_scoring}
# ppr = points per reception
ppr <- 0.5
pass_yards <- 0.04
pass_td <- 4
int <- -1
rush_yards <- 0.1
rush_td <- 6
# rpt_yards = reception yards
rpt_yards <- 0.1
rpt_td <- 6
return_td <- 6
# off_fmb_td = offensive fumble return TD. Doesn't happen too often, but just in case. 
off_fmb_td <- 6
# two_pt = two-point conversion
two_pt <- 2
fumble <- -2
```

And now, defensive.
```{r def_scoring}

```


# Data Import
We need some data to analyze, so we scraped data from [PFR](www.pro-football-reference.com). This can be found and run in the data_scrape.R script. 

```{r data_import, message=FALSE}
pass <- read_csv("https://raw.githubusercontent.com/jakeberberian/fantasy-football/master/data/pass.csv")

rush <- read_csv("https://raw.githubusercontent.com/jakeberberian/fantasy-football/master/data/rush.csv")

receive <- read_csv("https://raw.githubusercontent.com/jakeberberian/fantasy-football/master/data/receive.csv")

fantasy <- read_csv("https://raw.githubusercontent.com/jakeberberian/fantasy-football/master/data/fantasy.csv")
```

# Data Clean

Let's look at our data and decide if there's anything specific we need to do to clean it. Since PFR has some formatting issues, we'll go in and clean those up. The first thing that PFR does is the duplicate the column headers every few rows, as it makes reading on the web much easier. We'll filter those out. 
```{r remove_headers}
remove_headers <- function(df) {
  df %>% 
    filter(GS != "GS")
}

data <- list(fantasy, pass, receive, rush) %>% 
  map(remove_headers)

fantasy <- data[[1]]
pass <- data[[2]]
receive <- data[[3]]
rush <- data[[4]]

rm(data)
```

Next, we see that some players have asteriks or plusses next to their names, to indicate All-Pro/All-Star status. We want to clean these out, such that it won't affect the naming conventions. 
```{r clean_names}
clean_names <- function(df) {
  
  
}

pass %>% 
  gsub(Player, "^.*?\\.")


```


```{r}
# quick check to compare ML times on laptop vs. PC
fantasyWR <- fantasy %>% 
  mutate(Age = as.numeric(Age), 
         GS = as.numeric(GS),
         Tgt = as.numeric(Tgt)) %>% 
  filter(FantPos == "WR")

set.seed(51)
train <- sample(nrow(fantasyWR), 0.7 * nrow(fantasyWR), replace = FALSE)
TrainSet <- fantasyWR[train, ]
ValidSet <- fantasyWR[-train, ]


```


```{r}
model1 <- randomForest(PPR ~ Age * GS * Tgt, data = TrainSet, importance = TRUE, do.trace = TRUE, na.action = na.omit)
```






